The Morality of Arbitrage

### 2017-05-22 Draft/draft2.tex
Updating draft2.

@@

\newpage
\singlespacing 
\bibliography{master.bib}

>>>>

The dictionary definition of a Dutch book is the following:

\begin{quote}
``A principle for dynamic decision-making situations that leads to a
sequence of bets finishing in an inescapable loss, as in the case of a
bookmaker always gaining from gambling on the outcome of horse
races.''\footnote{See the Routledge Dictionary of Economics entry on
  ``Dutch books.''}.
\end{quote}

@@

\newpage
\singlespacing 
\bibliography{master}
